# `r a.title`

### *Nathan Siemers, Bristol-Myers Squibb*

`r Sys.Date()`

```{r , results = 'asis', echo = FALSE }

library(knitr)

```

### Cohort, Gating: `r my.title(input)`

### Genes plotted: `r input$geneplot`

### `r default.filterby`: `r paste(input$filteredby, collapse = ';')`


*`r paste("PI:", a.PI)`*

*`r paste("Contributors:", a.credits )`*


`r a.desc`

`r a.methods`

## Fauxflow Plot

```{r plot1, dpi = 100, fig.width = 20, fig.height = 20, warning = FALSE, results = 'hide', echo = FALSE, message = FALSE, warning = FALSE}

fun_plot1(l.input)

```

```{r , echo = FALSE, results = 'asis'}

if ( input$maketable ) {
    cat('\n\n##Table of correlations.\n\n')
}

```

```{r , echo = FALSE, results = 'show'}

if ( input$maketable ) {

kable( fun_table1(input) )

}



```{r, echo = FALSE, results = 'asis'}

if ( input$combogates ) {
    cat('\n\n##Population table.\n\n')

}

```

```{r , echo = FALSE, results = 'show'}

if ( input$combogates ) {
    kable( combogates(input) )
}


```
