# `r sc_env$title`

### *Nathan Siemers*

`r Sys.Date()`

```{r , results = 'asis', echo = FALSE }

library(knitr)

```

### Cohort, Gating: `r my.title(input)`

### Genes plotted: `r input$genelist`

### `r sc_env$default.filterby`: `r paste(input$filtervalues, collapse = ';')`


*`r paste("PI:", sc_env$PI)`*

*`r paste("Contributors:", sc_env$credits )`*


`r sc_env$desc`

`r sc_env$methods`

## Fauxflow Plot

```{r plot1, dpi = 100, fig.width = 20, fig.height = 20, warning = FALSE, results = 'hide', echo = FALSE, message = FALSE, warning = FALSE}

warning('plotting')
warning(l.input)
##fun_plot1(l.input)
fun_plot1(input)

```

```{r , echo = FALSE, results = 'asis'}

if ( input$maketable ) {
    cat('\n\n##Table of correlations.\n\n')
}

```

```{r , echo = FALSE, results = 'show'}

if ( input$maketable ) {

kable( fun_table1(input) )

}



```{r, echo = FALSE, results = 'asis'}

if ( input$combogates ) {
    cat('\n\n##Population table.\n\n')

}

```

```{r , echo = FALSE, results = 'show'}

if ( input$combogates ) {
    kable( combogates(input) )
}


```
